---
title: 'Overview of Reddit Users Using Phrase'
author: "JJB"
date: "11/14/2018"
output: md_document
---

# Obtain Data

Run on [Google BigQuery](https://console.cloud.google.com/bigquery).

```sql
SELECT author, body
FROM `fh-bigquery.reddit_comments.20*`
WHERE subreddit = 'UIUC'
AND REGEXP_CONTAINS(body, r'(?i)ask your advisor')
```

Save data as a CSV. The data used for this analysis can be found in the [`data/`](data/) folder.

# Post processing

Once we have the data, let's bring it into _R_.

```{r}
# Load in the Data
comments = read.csv("data/results-20181114-075107.csv")
```

## User Overview

Let's quickly take a peak at the different contributors using this phrase.

```{r}
# Figure out user counts
count_users = table(comments$author)

# Number of Unique Users
n_users_unique = length(count_users)

# Obtain a leaderboard of comments.
top_users = sort(count_users, decreasing = TRUE)

# Get name
top_username = names(top_users)[1]
top_user_posts =  top_users[1]

```

```{r echo = FALSE}
format_reddit_username = function(user) {
  paste0("[/u/", user,"](https://reddit.com/u/", user, ")")
}
```


There were **`r n_users_unique`** of users who used a variation of the phrase
"Ask your advisor". The user with the highest amount of comments was 
**`r format_reddit_username(top_username)`** who had **`r top_user_posts`**.

All users with at least 4 posts containing the phrase are listed next in a
descending order.

```{r, echo = FALSE}
cream_of_crop = as.data.frame(top_users[top_users >= 4])
names(cream_of_crop) = c("Username", "Frequency")
# Generate knitr table
knitr::kable(cream_of_crop)
```

## Amount of Words Used Per Post

```{r message=FALSE}
# Figure out user counts
library("dplyr")

comments %>%
  group_by(author) %>%
  summarise(mean_nwords = mean(stringr::str_count(body, "\\S+")),
            n_entries = n()) %>%
  arrange(desc(n_entries), desc(mean_nwords)) %>%
  filter(n_entries >= 4) %>%
  knitr::kable()
```

